---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TagR

<!-- badges: start -->
<!-- badges: end -->

## What is TagR?

TagR is SHARE's R package for topic tagging using machine learning. Using predefined topics and a labelled data set, it allows the user to find the probability that an unlabelled post belongs to a particular topic.

This package is used by running through the following steps:

* Pre-process the text data
* Conduct exploratory data analysis 
* Create document-term matrices
* Bind any numerical variables to the document-term matrices
* Find an optimal set of parameters for the Xgboost model for each topic
* Train a model for each topic and predict the probabilities that each post in the unlabelled data set belongs to such topic
* Build an explainer that helps the user visualise how the Xgboost model makes its predictions

## Installation

You can install the released version of TagR from [CRAN](https://CRAN.R-project.org) with:


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(TagR)
## basic example code
```

