---
title: "full_IT_DEV_example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{full_IT_DEV_example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.align = "center")
```

```{r setup}
library(pander)
library(TagR)
```

This notebook provides a full example of how a user can utilise the TagR package.

We will go through the following steps:

1. Pre-process the text data
1. Conduct exploratory data analysis
1. Create document-term matrices
1. Bind  numerical variables to the document-term matrices
1. Find an optimal set of parameters for the Xgboost model for each type of author
1. Train a model for each author type and predict the probabilities that each post in the unlabelled data set belongs to such author
1. Build an explainer that helps to visualise how the Xgboost model makes its predictions

## The Data

The labelled dataset consists of 644 tweets where the author has been identified as either an IT professional, a developer, or neither.
The unlabelled dataset consists of 644 tweets where the author has not yet been identified.

```{r}
labelled <- TagR::labelled
unlabelled <- TagR::unlabelled
```

The labelled dataset looks like the following:

```{r, results = "asis"}
pander::pandoc.table(names(labelled))
```



